A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-10 paper.tex
Remove sentence that references missing tables

@@

@@

@@

\subsubsection{Issues in End-to-End-Encryption}
E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, there are some challenges in the E2EE process. Tampering the messages which have conducted E2EE would be a challenging mission. However, spamming would be the critical issue participants may meet under this architecture. It is risky for an edge device connects to a tangle-accelerator which is operated by unknown third-party. Sharing Channel Chain ownership with an unknown third-party would allow them to spam on the MAM Channel Chain. Spam would cause subscribers wasting plenty of time on decrypting useless messages. To prevent edge devices from the annoying attack, connecting to an known, trustworthy tangle-accelerator would be the easiest solution.

@@

\subsection{MAM vs. the delegated MAM}
\label{section:smart_contract_evaluation}
What follows is an account of performance comparison between MAM and delegated MAM (E2EE) for different payload sizes. Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps. Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly. In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too. The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.

@@

It the Fig.~\ref{fig:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for low-level embedded system to send authenticated streaming data. Next, regarding the trend of the two lines, the performance of E2EE is obviously more steady than MAM in the given range. The bump of MAM performance around 750 bytes proves this point. Moreover, the performance of E2EE is almost under constant time, but MAM takes linear time on encrypting messages.

@@

In the subscription-based data trading, there are some issues that worth discussing and improving. Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{section:smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation. Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers. Second, brokers are the key to operate a stable system, since they are irreplaceable either from the view of architecture design or trading procedures. However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.

>>>>

\subsection{Paper Organization}
The rest of this paper is organized as follows. In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures and distributed data storage are analyzed. In Section~\ref{section:design_thinking}, the componets of proposed subscription-based data trading architecture is illustrated. In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices. In Section~\ref{section:trading_model}, the trading models of proposed architecture are well explained. The analysis results are given in Section~\ref{section:evaluation}. Finally, we conclude the paper in Section~\ref{section:conclusion}.

@@

\subsection{Distributed Storage System}
Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider. Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network. Filecoin \cite{FileCoin} in Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage. IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network. However, no cryptographic system is applied for user-uploaded files. Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts. Files are duplicated in multiple nodes to prevent data loss.

@@

\subsubsection{Communication Protocol}
In the following sections, we refer the low-level devices as \textbf{endpoint}s. MQTT\cite{MQTT} is chosen as the communication protocol, which requires fewer TCP packets and less traffic. The topic-based pub/sub pattern and lightweight packet that MQTT adopts would undoubtedly play an important role on endpoints with limited bandwidth. The pub/sub model decouples publishers and subscribers in many ways:

\begin{itemize}
    \item Space decoupling: Both publishers and subscribers don't need to know each other.
    \item Time decoupling: Publishers and subscribers do not need to be active at the same time.
    \item Synchronization decoupling: Operations are decoupled from the publishers and subscribers. The publishers do not need to be alive until the response arrives. Messages from publisher can be served as send-and-forget fashion.
\end{itemize}

@@

\subsubsection{Register with Tangle-accelerator}
User with channel seed can acquire channel chain ownership. Seed is generated by unique hardware information on edge device, so it should be transmitted to tangle-accelerator which allows it to publish messages on MAM channel chain. Asymmetric encryption is utilizing during the process of exchanging seed. Digital signature should be taken at the same time to ensure data integrity. Once the seed has been successfully exchanged, edge device is successfully registered on the specific tangle-accelerator. Thus, seed will not be exposed during communication after an edge device is successfully registered.

\subsubsection{Issues in End-to-End-Encryption}
E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met two challenges in the E2EE process:

\paragraph{Linear Time to Read Message}
It is linear time to decrypt message instead of constant time. Nevertheless, there is one way to speed up the message decryption process. A subscriber can fetch multiple MAM messages with one API call, then the subscriber can decrypt the ciphertext at local side. This procedure can reduce the time spending on internet communication.

\paragraph{Spam on Message Channel Chain}
Tampering the messages which have conducted E2EE would be a challenging mission. However, spamming would be the critical issue participants may meet under this architecture. It is risky for an edge device connects to a tangle-accelerator which is operated by unknown third-party. Sharing Channel Chain ownership with an unknown third-party would allow them to spam on the MAM Channel Chain. Spam would cause subscribers wasting plenty of time on decrypting useless messages. To prevent edge devices from the annoying attack, connecting to an known, trustworthy tangle-accelerator would be the easiest solution.

@@

\subsection{MAM vs. the delegated MAM}
\label{section:smart_contract_evaluation}

\subsubsection{Experiment}
Applying remote PoW greatly reduce the elapsed time. Channel creation is the next primary barrier for low-level devices to broadcast MAM message. With employing delegated MAM and E2EE, MAM channel creation would be delegated by tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices. What follows is the performance comparison between MAM and delegated MAM (E2EE) for different payload sizes. Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps. Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly. In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too. The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values. In the E2EE protocol framework, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.

@@

It the Fig.~\ref{fig:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for low-level embedded system to send authenticated streaming data. Next, regarding the trend of the two lines, the performance of E2EE is obviously more steady than MAM in the given range. The bump of MAM performance around 750 bytes proves this point.

\subsubsection{Time Complexity}
With given E2EE protocol framework. ECDSA would take constant time under our situation, since the string needed to be signed is in fixed length. HMAC and AES-CBC are the procedures that cost most of the elapsed time. Time complexity of HMAC with SHA-256 is O(n).\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is O(n), too. Therefore, the E2EE protocol framework takes only linear time. Applying mature cryptographic functions (e.g. SHA-256, AES-CBC, etc) apparently makes E2EE perform with smaller slope.

\subsection{Smart Contract}
In this experiment, we investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix that we can define the minimum cost, which data providers should pay in order to launch a product and processing a trade.  On top of this evaluation, data providers can consider how to set the price to eventually generate profits. The estimated cost is in Ether, which is 238 USD at the time of writing, yet the price is dynamic from time to time. To conquer this condition, the authors in \cite{MindMyValue} suggested to analyze with a fixed range of Gas price,  yet the main drawback of low Gas price is the increase of time required before a transaction is validated. According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price. The Gas usage estimation is shown in Table.~\ref{tab:gas}.

\begin{table*}[h]
	\caption{Gas consumption for each function of Product Contract}
	\label{tab:gas}
	\centering
	\resizebox{0.5\textwidth}{!}{
	\begin{tabular}{|c|c|c|c|}
		\hline
		\textbf{function} & \textbf{sender} & \textbf{Gas used} \\
		\hline
		generate contract & broker & 2558980 \\ 
		subscribe product & consumer & 72259 \\ 
		upload hashed key & provider & 68276  \\ 
		upload encryption key to consumer & provider & 86614 \\ 
		upload certified key & broker & 131535 \\
		update amount of uploaded data & broker & 32157 \\
		unsubscribe & consumer & 8234 \\
		request refund & consumer & 12067 \\
		withdraw & broker & 11313 \\
		\hline
	\end{tabular}
	}
\end{table*}

Note that data uploading is only related to MAM operations on IOTA, which does not require any fees. Therefore, the Gas estimation only includes trading processes. Creating a Product Contract (Listing \ref{lst:constructor}) costs the most Gas (0.164 - 0.596 Ether), providers should have enough Ethers to launch the product at start. Functions (Listing \ref{lst:key_exchange} (0.012 - 0.044 Ether) and Listing \ref{lst:key_certification}) (0.022 - 0.0834 Ether) that are related to key certification and key exchange need a lot of gas as well. Storage on blockchain is expensive. For instance, an SSTORE operation may cost 20000 gas when the value is set to non-zero from zero according to Ethereum Yellow Paper\cite{Ethereum}. However, in our trading model, we preserve a lot of information in Product Contract in order to record as more details as possible during trading procedures, such as ciphertexts,  signatures during key certification and key exchange. Especially, in the key exchange protocol, it takes several steps of communications between brokers, data providers and data consumers via storing states to Product Contract. Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys. However, using zero-knowledge protocol is out of the scope of this paper.

Base on Gas estimation in Table.~\ref{tab:gas}, we calculate the exact Ether with Formula~\ref{equa:ether_calculation} that data providers and data consumers need during the trade in Table.~\ref{tab:ether}. We combine the Gas usage of providers and brokers, since the brokerage fee is also a critical cost to sustain the trade, which providers should considered. We conclude the four situations during the trading process: w/o refund and unsubscribe, w/ refund only, w/unsubscribe and w/ refund and unsubscribe. The condition of w/o refund and unsubscribe represents the basic cost of  triggering regular functions, such as launch, add encryption key.

\begin{equation}
\label{equa:ether_calculation}
Ethers = Gas \ Price \times Gas \ Amount
\end{equation}

When a consumer request a refund, he/she need to pay 0.0003 Ether additionally. Then if the refund established, all participants will withdraw the payment, which is already included in the basic cost. Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers. However, the data provider need to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the amount of remaining subscribers. This would cost data providers a lot if the unsubscription is frequent or many consumers subscribe to the data product. Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important. An alternative strategy coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract. Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.

\begin{table*}[h]
	\caption{Data Price Estimation}
	\label{tab:ether}
	\centering
	\resizebox{0.8\textwidth}{!}{
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		\textbf{condition} & \textbf{sender} & \textbf{\makecell{minimum price \\ (Ether)}} & \textbf{\makecell{minimum price \\ (USD)}} & \textbf{\makecell{maximum price \\ (Ether)}} & \textbf{\makecell{maximum price \\ (USD)}} \\
		\hline
		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
		 & consumer & 0.00061 & 0.145 & 0.0022 & 0.527\\
		\hline
		\multirow{2}{*}{w/ refund} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
		 & consumer & 0.00069 & 0.166 & 0.0025 & 0.603 \\
		\hline
		\multirow{2}{*}{w/ unsubscribe} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N \\
		 & consumer & 0.00067 & 0.159 & 0.0024 & 0.579 \\
		\hline
		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N\\
		 & consumer & 0.0007 & 0.180 & 0.0027 & 0.655 \\
		\hline
	\end{tabular}
	}
\end{table*}

@@

In the subscription-based data trading, there are some issues that worth discussing and improving. Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{section:smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation. Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers. Second, brokers are the key to operating a stable system, since they are irreplaceable either from the view of architecture design or trading procedures. However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.
